\section{Conclusion and Future Work}

The complexity of modern systemic trading and quantitative analysis necessitates tools that match the scope of raw financial data produced globally. We have demonstrated the framework for an \textbf{Agentic Quant Researcher}---a fast, parallelized, and highly accurate AI system leveraging Retrieval-Augmented Generation capabilities.

With a fully implemented backend infrastructure processing unstructured SEC documentation, parsing numerical market datasets, and separating findings effectively using recursive vectoring protocols, LLM orchestration produces highly actionable and robust trading suggestions. The combination of Claude-driven reasoning alongside deterministic, pre-trained embedded pipelines creates an end-to-end multi-agent firm with a pronounced competitive analytics edge in modern finance.

The reduction in research latency from hours to seconds provides a distinct informational advantage in a market where reaction time is paramount. However, we view this architecture as merely the foundation layer for fully autonomous agency.

Future work will focus on three primary avenues of expansion:
\begin{enumerate}
    \item \textbf{Live Autonomous Execution:} Deploying the Agents within a live paper-trading environment via the Alpaca API. This would allow the Orchestrator to monitor live tick data and dynamically rebalance the portfolio without human intervention based on its synthesized confidence scores.
    \item \textbf{Alternative Data Ingestion:} Expanding the vector embeddings beyond regulatory filings to include unverified social sentiment from platforms like Reddit and X (Twitter). This would require training the Sector agent to distinguish between retail momentum noise and credible insider signaling.
    \item \textbf{Peer Benchmarking Modules:} Introducing a fourth sub-agent specifically dedicated to comparative analysis. This agent would automatically query a company's three closest competitors within its Pinecone namespace to provide relative valuation grading rather than strictly absolute valuation.
\end{enumerate}
